## Feature Analysis

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(data.table)
library(lmtest)
library(sandwich)
library(stargazer)
library(dplyr)
library(DataExplorer)
library(MatchIt)
library(cobalt)
library(ggplot2)

# Insert the function to *tidy up* the code when they are printed out	
library(knitr)

#opts_chunk$set(tidy.opts=list(width.cutoff=60), tidy=TRUE)
``` 

```{r Check if d exists}
tryCatch(
  {
    nrow(d)
  },
  error = function(e) {
    print("d variable not found, cannot proceed further!")
    stop(e)
  }
)
```

### Check Balance of Control & Treatment Assignments
```{r}
# Ratio of Treatment and Assignment (After removal of outliers and abnormal data)
d[, .(count=.N), by = list(TreatmentAssignment)]
```

### Check Covariates For Missing Data
```{r}
# Proportion of missing values in covariates
plot_missing(d[, c('YearOfBirth', 'GenderCategory','Gender','IsEnglishFirstLanguage','Race','CountryOfResidence','StateOfResidence','RoleAtBerkeley','IsTransferStudent','YearsAtBerkeley','DidEarnMoneyLastYear','EmploymentStatus','IncomeIn2020','HighestDegreeReceived','PoliticalAffiliation','ReligiousAffliation','BookFormatPurchasedMostOften','FrequencySocialMediaAccess','FrequencySocialMediaPosting','ClassLevel','GenderCGSurvey','HasServedInCG','HasServedInAnyOtherUniformedService','PlaceboPreTestColleagueAffinity','PlaceboPostTestColleagueAffinity')])
```

>We are going to ignore last 5 variables that have too many missing values.

```{r}
# Covariate balance check (The only continuous variable: YearOfBirth)
# We have already removed outliers and abnormal values in feature engineering
plot_density(d$YearOfBirth)
```

>Most of respondents are around 20 years old.

### Covariate Balance Check
```{r}
# Covariate balance check (Overall)
plot_bar(d[, c('GenderCategory','IsEnglishFirstLanguage','HighestDegreeReceived','Race','RoleAtBerkeley','DidEarnMoneyLastYear','EmploymentStatus','PoliticalAffiliation','ReligiousAffliation','BookFormatPurchasedMostOften','FrequencySocialMediaAccess','FrequencySocialMediaPosting','ClassLevel','GenderCGSurvey','HasServedInCG','HasServedInAnyOtherUniformedService','CountryOfResidence')], nrow=2, ncol=1)
```

>Most of the respondents have never served in uniformed service before, so it is hard to say that their reply will reflect the actual treatments that we hope to observe in the CG survey. Almost all respondents are from the United States. Around 66% of the respondents are female, half of them are Asian. Roughly half of the respondents are democrats, and only 5.3% of them are republicans. The main source of data is xlab (undergraduate Berkeley students). It has to be kept in mind that the treatment effects observed here would be vastly different than those observed in the actual survey.

```{r}
# Covariate balance check (Control vs Treatment)
matchO <- matchit(TreatmentAssignment ~ YearOfBirth + GenderCategory + Race + IsEnglishFirstLanguage + HighestDegreeReceived + DidEarnMoneyLastYear +
                     EmploymentStatus + PoliticalAffiliation + ReligiousAffliation + BookFormatPurchasedMostOften + FrequencySocialMediaAccess +
                     FrequencySocialMediaPosting + ClassLevel + GenderCGSurvey + HasServedInCG + HasServedInAnyOtherUniformedService, 
                   data = d,
                   method = NULL)
summary(matchO)
```

```{r warning=FALSE}
bal.plot(matchO, var.name = "YearOfBirth")
bal.plot(matchO, var.name = "GenderCategory") + scale_x_discrete(guide = guide_axis(n.dodge=2))
bal.plot(matchO, var.name = "Race") + scale_x_discrete(guide = guide_axis(n.dodge=3))
```

```{r warning=FALSE}
matchO <- matchit(TreatmentAssignment ~ YearOfBirth + GenderCategory + Race,
                   data = d,
                   method = NULL)
love.plot(matchO, stats='mean.diffs', binary='std')
love.plot(matchO, stats='variance.ratios')
```

>In conclusion, we observe that we do have overall covariate balance because the standardized mean differences are `on average 0.3 units or less when compared with a 0 mean difference`. This is satisfactory in terms of proceeding with the analysis for now. We cannot change much here since we do not have the luxury to reconduct / randomize the survey participants again.  