## Feature Engineering

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# Clean up the work space before we begin	
rm(list = ls()); set.seed(1)
library(data.table)
library(lmtest)
library(sandwich)
library(stargazer)
library(dplyr)
``` 

```{r}
d <- fread("data.csv",  na.strings=c("","NA"))

# head(d)
```

```{r}
# display number of columns
length(d[0])
```

```{r}
# ResponseID is our primary key for the table as it is unique for each row and is guaranteed to be present
nrow(d[, .(count=.N), by = list(ResponseID)]) == nrow(d)
```

```{r}
d[, .(count=.N), by = list(ResponseType)]
```

```{r}
d[, .(count=.N), by = list(Finished)]
```

```{r Utility Functions}
# gets a row by the field "Name" in dataframe "data"
getRowByName <- function(name, data) {
  return (data[data$Name == name, ]) 
}

# gets a row by the field "TreatmentCol" in dataframe "data"
getRowByTreatmentCol <- function(num, data) {
  return (data[data$TreatmentCol == paste("TreatmentQ", num, sep=""), ]) 
}

# gets a row by the field "ControlCol" in dataframe "data"
getRowByControlCol <- function(num, data) {
  return (data[data$ControlCol == paste("ControlQ", num, sep=""), ]) 
}

# gets a row by the field "ResponseID" in dataframe "data"
getRowByResponseID <- function(responseId, data) {
  return (data[data$ResponseID == responseId, ]) 
}

# are all treatment questions NA (condition for participant being in control group)
areAllTreatmentQNA <- function(data, rowNum) {
  return (is.na(data[rowNum]$TreatmentQ1) & is.na(d[rowNum]$TreatmentQ2) & is.na(d[rowNum]$TreatmentQ3) &   is.na(d[rowNum]$TreatmentQ4) & is.na(d[rowNum]$TreatmentQ5) & is.na(d[rowNum]$TreatmentQ6))
}

# are all control questions NA (condition for participant being in treatment group)
areAllControlQNA <- function(data, rowNum) {
  return (is.na(data[rowNum]$ControlQ1) & is.na(d[rowNum]$ControlQ2) & is.na(d[rowNum]$ControlQ3) &   is.na(d[rowNum]$ControlQ4) & is.na(d[rowNum]$ControlQ5) & is.na(d[rowNum]$ControlQ6))
}

# gets number of treatment columns that are NA 
getSumTreatmentQNA <- function(data, rowNum) {
  
  someTreatmentNA = c(is.na(data[rowNum]$TreatmentQ1), is.na(d[rowNum]$TreatmentQ2),  is.na(d[rowNum]$TreatmentQ3), is.na(d[rowNum]$TreatmentQ4), is.na(d[rowNum]$TreatmentQ5), is.na(d[rowNum]$TreatmentQ6))
  
  return (sum(someTreatmentNA))
}

# gets number of control columns that are NA 
getSumControlQNA <- function(data, rowNum) {
  
  someControlNA = c(is.na(data[rowNum]$ControlQ1), is.na(d[rowNum]$ControlQ2), is.na(d[rowNum]$ControlQ3),   is.na(d[rowNum]$ControlQ4), is.na(d[rowNum]$ControlQ5), is.na(d[rowNum]$ControlQ6))
  
  return (sum(someControlNA))
}

# if all 12 columns of treatment and control are NA, then the row is invalid
# represents a likely non-complier (never taker)
isInvalidRow <- function(data, rowNum) {
  return(getSumControlQNA(data, rowNum) + getSumTreatmentQNA(data, rowNum) == 12)
}

# if person was assigned to either treatment or control, but didn't end up answering all questions
# if person didn't answer any of the questions, then also they are considered an attritor
isAttritedRow <- function(data, rowNum) {
  cols = getSumControlQNA(data, rowNum) 
  result = (cols < 6 & cols > 0)
  if (result) {
    return (result)
  }
  
  cols = getSumTreatmentQNA(data, rowNum)
  result = (cols < 6 & cols > 0)
  return (result | isInvalidRow(data, rowNum))
}

# we cannot have some NA in both treatment and control
isInvalidTreatmentAssignment <- function(data, rowNum) {
  controlNa = getSumControlQNA(data, rowNum) 
  treatmentNa = getSumTreatmentQNA(data, rowNum)
  return ((controlNa > 0 & controlNa < 6) & (treatmentNa > 0 & treatmentNa < 6))
}

# generating random numbers from low to high for fake treatment/control responses
generateRandomIntNums <- function(n, mean, sd, low=1, high=7) {
  
  nums = mean + sd * scale(rnorm(n))
  # numbers must be 1-5
  for (i in 1:nrow(nums)) {
    
    # arbitrarily choose floor or ceiling for that number (since response must be integer)
    if(sample(c(0,1), size =1))  {
      nums[i] = ceiling(nums[i])
    }
    else {
      nums[i] = floor(nums[i]) 
    }
    
    # bound number between 1-7
    if(nums[i] < low) {
      nums[i] = low
    }
    
    if(nums[i] > high) {
      nums[i] = high
    }
  }
  
  return(nums[1:n])
}
```

## Create meta data for control & treatment group

```{r}
nameResumeBinding <- data.table(
  Name  = c("Bradley Meyer", "Reginald Washington", "Kirsten Schmidt", "Gwendolyn Jackson"),
  Race = c("White", "Black", "White", "Black"),
  Gender = c("Male", "Male", "Female", "Female"),
  RaceGender = c("WM", "BM", "WF", "BF"),
  ResumeId   = c(1, 2, 3, 4)
)
```

```{r}
treatmentBinding <- data.table(
  LeftPersonName  = c("Bradley Meyer", "Bradley Meyer", "Bradley Meyer", "Kirsten Schmidt", "Reginald Washington", "Kirsten Schmidt"),
  RightPersonName = c("Reginald Washington", "Kirsten Schmidt", "Gwendolyn Jackson", "Reginald Washington", "Gwendolyn Jackson", "Gwendolyn Jackson"),
  TreatmentCol = c("TreatmentQ1", "TreatmentQ2", "TreatmentQ3", "TreatmentQ4", "TreatmentQ5", "TreatmentQ6")
)
```

```{r}
treatmentMetadata <- data.table(treatmentBinding)
n <- nrow(treatmentMetadata)

# fill dummy values to create column names
for (i in 1:n) {
  treatmentMetadata$LeftPersonRace = "test"
  treatmentMetadata$LeftPersonGender = "test"
  treatmentMetadata$LeftPersonRaceGender = "test"
  treatmentMetadata$LeftPersonResumeId = "test"
   
  treatmentMetadata$RightPersonRace = "test"
  treatmentMetadata$RightPersonGender = "test"
  treatmentMetadata$RightPersonRaceGender = "test"
  treatmentMetadata$RightPersonResumeId = "test"
}

# iterate through left name and fill left person metadata
for (i in 1:n) {
  row <- getRowByName(treatmentMetadata[i]$LeftPersonName, nameResumeBinding)
   
  treatmentMetadata[i]$LeftPersonRace = row$Race
  treatmentMetadata[i]$LeftPersonGender = row$Gender
  treatmentMetadata[i]$LeftPersonRaceGender = row$RaceGender
  treatmentMetadata[i]$LeftPersonResumeId = row$ResumeId
}

# iterate through right name and fill right person metadata
for (i in 1:n) {
  row <- getRowByName(treatmentMetadata[i]$RightPersonName, nameResumeBinding)
   
  treatmentMetadata[i]$RightPersonRace = row$Race
  treatmentMetadata[i]$RightPersonGender = row$Gender
  treatmentMetadata[i]$RightPersonRaceGender = row$RaceGender
  treatmentMetadata[i]$RightPersonResumeId = row$ResumeId
}
```

```{r}
controlBinding <- data.table(
  LeftPersonResumeId  = c(1, 1, 1, 3, 2, 3),
  RightPersonResumeId = c(2, 3, 4, 2, 4, 4),
  ControlCol = c("ControlQ1", "ControlQ2", "ControlQ3", "ControlQ4", "ControlQ5", "ControlQ6")
)
```


## Treatment & Control assignment; Attritor check

```{r}
# treatment and control assignment
n <- nrow(d)

# have valid columns for treatment assignment and attrition
d$TreatmentAssignment = NA
d$IsAttrited = NA
d$IsNeverTaker = NA

for (i in 1:n) {
  # row <- getRowByResponseID(d[i]$ResponseID, d)
  
  control <- areAllTreatmentQNA(d, i)
  treatment <- areAllControlQNA(d, i)
  isInvalid <- isInvalidRow(d, i)
  isAttrited <- isAttritedRow(d, i)
  isInvalidTreatmentAssigned <- isInvalidTreatmentAssignment(d, i)
  
  # print(c(control, treatment, isInvalid, isAttrited, isInvalidTreatmentAssigned))
  if (isInvalid | isInvalidTreatmentAssigned) {
    
    if (isInvalidTreatmentAssigned) {
      e = sprintf("Row %s has invalid treatment assignment", i)  
      stop(e)
    }
    
    if (isInvalid) {
      sprintf("Row %s has no responses in treatment and control columns", i)  
    }
    
    d[i]$TreatmentAssignment = NA
    
  }
  else {
    
    if (treatment & control) {
      e = sprintf("Both treatment and control are true! This should never happen! Error found in row %s", i)
      stop(e)
    }
    
    d[i]$TreatmentAssignment = treatment  
  }
  
  d[i]$IsAttrited = isAttrited
  d[i]$IsNeverTaker = isInvalid
  
  # special case, if we find attrition only, then we need to re-assign treatment  
  if (isAttrited & !(isInvalid | isInvalidTreatmentAssigned)) {
    
    numNa = getSumTreatmentQNA(d, i)
    treatment = numNa > 0 & numNa < 6    
    d[i]$TreatmentAssignment = treatment      
  
  }
}
```

```{r}
d[, .(count=.N), by = list(TreatmentAssignment)]
```

```{r}
d[, .(count=.N), by = list(IsAttrited)]
```

```{r}
# do a sanity check of who we think are "attritors" vs what qualtrics thinks are "attritors"
responseIDsAttrited = d[IsAttrited == TRUE, ResponseID]
responseIDsBad = d[Finished == FALSE | ResponseType != "IP Address", ResponseID]
responseIDsUnFinishedOnly = d[Finished == FALSE, ResponseID]

# there seem to be a mismatch in what we consider attrited vs what Qualtrics thinks is attrited
length(responseIDsAttrited)
length(responseIDsBad)
length(responseIDsUnFinishedOnly)

# Number of common elements between these sets
length(intersect(responseIDsAttrited, responseIDsBad))
length(intersect(responseIDsAttrited, responseIDsUnFinishedOnly))

# setdiff tells us the response IDs that exist in the first list, but dont exist in the 2nd list

print("These are the respondents we think are attritors but Qualtrics thinks are not attritors")
setdiff(responseIDsAttrited, responseIDsBad)

print("These are the respondents Qualtrics think are attritors but we think are not")
setdiff(responseIDsBad, responseIDsAttrited)

setdiff(responseIDsAttrited, responseIDsUnFinishedOnly)
setdiff(responseIDsUnFinishedOnly, responseIDsAttrited)

# Examining the list that qualtrics thinks are attritors, we see in fact they are not attritors, so we'll stick to our definition
# example: d[ResponseID == "R_1E6Y207cj3ZVUY0"]
```

```{r}
# Remove records that we think are attritors
d <- d[IsAttrited == FALSE]
nrow(d)
```

## Filter data with low answering time

```{r}
# We also check the average time people take to evaluate 6 pairs of resumes.
# FC: first click; LC: last click; PS: page submit; CC: click count

d <- d[,  AvgTime := as.double(.N)]

n <- nrow(d)
for (i in 1:n){
  if (d[i]$TreatmentAssignment == TRUE){
    d[i]$AvgTime <- (d[i]$TimePS_TreatmentQ1 + d[i]$TimePS_TreatmentQ2 + d[i]$TimePS_TreatmentQ3 + d[i]$TimePS_TreatmentQ4 + d[i]$TimePS_TreatmentQ5 + d[i]$TimePS_TreatmentQ6)/6
  }
  else {
    d[i]$AvgTime <- (d[i]$TimePS_ControlQ1 + d[i]$TimePS_ControlQ2 + d[i]$TimePS_ControlQ3 + d[i]$TimePS_ControlQ4 + d[i]$TimePS_ControlQ5 + d[i]$TimePS_ControlQ6)/6
  }
}

hist(d[TreatmentAssignment==0]$AvgTime, 
     breaks = 20, 
     main = 'Histogram for averge answering time for control group questions', 
     xlab='Averge answering time')

hist(d[TreatmentAssignment==1]$AvgTime, 
     breaks = 100, 
     main = 'Histogram for averge answering time for treatment group questions', 
     xlab='Averge answering time')

print('Median of averge answering time for control group questions')
median(d[TreatmentAssignment==0]$AvgTime)

print('Median of averge answering time for treatment group questions')
median(d[TreatmentAssignment==1]$AvgTime)
```

```{r}
# Averge answering time is relatively short.
# Here we remove any record with an average answering time less than 10 seconds.
d <- d[AvgTime>=10]
nrow(d)
```

## Filter data with YearOfBirth
```{r}
# Check for outliers and abnormal values
unique(d$YearOfBirth)
```

There are outliers such as 25 and 2020, as well as abnormal values such as country names.

```{r}
# Remove outliers and abnormal values
d <- d[, YearOfBirth:=as.integer(YearOfBirth)]
d <- d[YearOfBirth<2015 & YearOfBirth>1950]
```

## Create Datasets to be used

```{r Utility Functions for Dataset Creation}
cols <- colnames(d)
coreColumns <- cols[!startsWith(cols, "TimeFC_") & !startsWith(cols, "TimeLC_") & !startsWith(cols, "TimePS_") & !startsWith(cols, "TimeCC_") & !startsWith(cols, "TreatmentQ") & !startsWith(cols, "ControlQ")]

getCoreColumnsDataset <- function() {
  return(d %>% select(one_of(coreColumns)))
}

getTreatmentDataset <- function(qNum) {
  treatmentqNum = paste("TreatmentQ", qNum, sep ="")
  treatmentSet = (d %>% select(one_of(coreColumns) | ends_with(treatmentqNum)))
  return (treatmentSet[TreatmentAssignment == TRUE, ])
}

getControlDataset <- function(qNum) {
  controlqNum = paste("ControlQ", qNum, sep ="")
  controlSet = (d %>% select(one_of(coreColumns) | ends_with(controlqNum)))
  return (controlSet[TreatmentAssignment == FALSE, ])
}
```

```{r}
dCore = getCoreColumnsDataset()

dTQ1 = getTreatmentDataset(1)
dTQ2 = getTreatmentDataset(2)
dTQ3 = getTreatmentDataset(3)
dTQ4 = getTreatmentDataset(4)
dTQ5 = getTreatmentDataset(5)
dTQ6 = getTreatmentDataset(6)

# sanity check to see all data sets are of the same size
nrow(dTQ1) == nrow(dTQ2)
nrow(dTQ2) == nrow(dTQ3) 
nrow(dTQ3) == nrow(dTQ4) 
nrow(dTQ4) == nrow(dTQ5) 
nrow(dTQ5) == nrow(dTQ6)

dCQ1 = getControlDataset(1)
dCQ2 = getControlDataset(2)
dCQ3 = getControlDataset(3)
dCQ4 = getControlDataset(4)
dCQ5 = getControlDataset(5)
dCQ6 = getControlDataset(6)

# sanity check to see all data sets are of the same size
nrow(dCQ1) == nrow(dCQ2)
nrow(dCQ2) == nrow(dCQ3) 
nrow(dCQ3) == nrow(dCQ4) 
nrow(dCQ4) == nrow(dCQ5) 
nrow(dCQ5) == nrow(dCQ6)
```

```{r}
# head(dTQ1)
```

### Assign Fake Treatment and Control Reponses (Optional)

>As we are aware, we had an error in the procedure around collecting data for our participants. Thus we will overwrite the data with fake responses so as to prove out our analysis methodology. Below we choose a `random number generator to generate responses from 1-7`. The rubric is as follows:

>`1: Strongly prefer left resume`

>`2: Prefer left resume`

>`3: Slightly prefer left resume`

>`4: Neutral (no preference on left or right resume)`

>`5: Slightly prefer right resume`

>`6: Prefer right resume`

>`7: Strongly prefer right resume`

```{r Generate Random Numbers And Assign to Response Column}

# We deliberately give fake treatment effects
dTQ1$TreatmentQ1 = generateRandomIntNums(nrow(dTQ1), 1, 1) # WM BM
dTQ2$TreatmentQ2 = generateRandomIntNums(nrow(dTQ2), 2, 1) # WM WF
dTQ3$TreatmentQ3 = generateRandomIntNums(nrow(dTQ3), 5, 1) # WM BF
dTQ4$TreatmentQ4 = generateRandomIntNums(nrow(dTQ4), 4, 1) # WF BM
dTQ5$TreatmentQ5 = generateRandomIntNums(nrow(dTQ5), 4, 1) # BM BF
dTQ6$TreatmentQ6 = generateRandomIntNums(nrow(dTQ6), 2, 1) # WF BF

# Note: means are typically underestimated
print("Treatment Means")
mean(dTQ1$TreatmentQ1)
mean(dTQ2$TreatmentQ2)
mean(dTQ3$TreatmentQ3)
mean(dTQ4$TreatmentQ4)
mean(dTQ5$TreatmentQ5)
mean(dTQ6$TreatmentQ6)

# We expect the control group to have no difference in left / right resumes (on average)
dCQ1$ControlQ1 = generateRandomIntNums(nrow(dCQ1), 3.5, 1)
dCQ2$ControlQ2 = generateRandomIntNums(nrow(dCQ2), 5, 2)
dCQ3$ControlQ3 = generateRandomIntNums(nrow(dCQ3), 6.5, 2)
dCQ4$ControlQ4 = generateRandomIntNums(nrow(dCQ4), 4, 1)
dCQ5$ControlQ5 = generateRandomIntNums(nrow(dCQ5), 4, 1)
dCQ6$ControlQ6 = generateRandomIntNums(nrow(dCQ6), 5, 1)

# Note: means are typically underestimated
print("Control Means")
mean(dCQ1$ControlQ1)
mean(dCQ2$ControlQ2)
mean(dCQ3$ControlQ3)
mean(dCQ4$ControlQ4)
mean(dCQ5$ControlQ5)
mean(dCQ6$ControlQ6)
```

```{r Join Treatment and Control Tables with Metadata}

addTreatmentMetadataToDataset <- function(dt, treatmentNum) {
  
  row = getRowByTreatmentCol(treatmentNum, treatmentMetadata)
  
  dt$LeftPersonName = row$LeftPersonName
  dt$LeftPersonRace = row$LeftPersonRace
  dt$LeftPersonGender = row$LeftPersonGender
  dt$LeftPersonRaceGender = row$LeftPersonRaceGender
  dt$LeftPersonResumeId = row$LeftPersonResumeId
    
  dt$RightPersonName = row$RightPersonName
  dt$RightPersonRace = row$RightPersonRace
  dt$RightPersonGender = row$RightPersonGender
  dt$RightPersonRaceGender = row$RightPersonRaceGender
  dt$RightPersonResumeId = row$RightPersonResumeId
  
  return(dt)
}

addControlMetadataToDataset <- function(dt, controlNum) {
  
  row = getRowByControlCol(controlNum, controlBinding)

  # only resume ID is available in the control group (by design)
  dt$LeftPersonName = NA
  dt$LeftPersonRace = NA
  dt$LeftPersonGender = NA
  dt$LeftPersonRaceGender = NA
  dt$LeftPersonResumeId = row$LeftPersonResumeId
  
  # only resume ID is available in the control group (by design)
  dt$RightPersonName = NA
  dt$RightPersonRace = NA
  dt$RightPersonGender = NA
  dt$RightPersonRaceGender = NA
  dt$RightPersonResumeId = row$RightPersonResumeId
  
  return(dt)
}

dTQ1 = addTreatmentMetadataToDataset(dTQ1, 1)
dTQ2 = addTreatmentMetadataToDataset(dTQ2, 2)
dTQ3 = addTreatmentMetadataToDataset(dTQ3, 3)
dTQ4 = addTreatmentMetadataToDataset(dTQ4, 4)
dTQ5 = addTreatmentMetadataToDataset(dTQ5, 5)
dTQ6 = addTreatmentMetadataToDataset(dTQ6, 6)

dCQ1 = addControlMetadataToDataset(dCQ1, 1)
dCQ2 = addControlMetadataToDataset(dCQ2, 2)
dCQ3 = addControlMetadataToDataset(dCQ3, 3)
dCQ4 = addControlMetadataToDataset(dCQ4, 4)
dCQ5 = addControlMetadataToDataset(dCQ5, 5)
dCQ6 = addControlMetadataToDataset(dCQ6, 6)

```

```{r, Finally we merge the treatment and control datasets, question by question}
# First, we notice that the 2 datasets dont have the same columns
print("Before convergence")
identical(colnames(dTQ1), colnames(dCQ1))
# Since the "Question columns" are named like "TimeFC_TreatmentQ1" in the treatment set and "TimeFC_ControlQ1" in the control set
# Thus we snap to naming these as "TimeFCQ" in both treatment and control. We add a dedicated column for Question Number as well to differentiate.
# The same naming convention goes for other columns - TimePS, TimeLS, TimeCC etc.

convergeTreatmentColumns <- function(dt, qNum) {
  names(dt)[names(dt) == paste("TimeFC_TreatmentQ", qNum, sep = "")] <- paste("TimeFCQ")
  names(dt)[names(dt) == paste("TimeLC_TreatmentQ", qNum, sep = "")] <- paste("TimeLCQ")
  names(dt)[names(dt) == paste("TimePS_TreatmentQ", qNum, sep = "")] <- paste("TimePSQ")
  names(dt)[names(dt) == paste("TimeCC_TreatmentQ", qNum, sep = "")] <- paste("TimeCCQ")
  names(dt)[names(dt) == paste("TreatmentQ", qNum, sep = "")] <- paste("ResponseQ")
  dt$QNum = qNum
  return(dt)
}

convergeControlColumns <- function(dt, qNum) {
  names(dt)[names(dt) == paste("TimeFC_ControlQ", qNum, sep = "")] <- paste("TimeFCQ")
  names(dt)[names(dt) == paste("TimeLC_ControlQ", qNum, sep = "")] <- paste("TimeLCQ")
  names(dt)[names(dt) == paste("TimePS_ControlQ", qNum, sep = "")] <- paste("TimePSQ")
  names(dt)[names(dt) == paste("TimeCC_ControlQ", qNum, sep = "")] <- paste("TimeCCQ")
  names(dt)[names(dt) == paste("ControlQ", qNum, sep = "")] <- paste("ResponseQ")
  dt$QNum = qNum
  return(dt)
}

dTQ1 = convergeTreatmentColumns(dTQ1, 1)
dCQ1 = convergeControlColumns(dCQ1, 1)

# now the test should pass 
print("After convergence")
identical(colnames(dTQ1), colnames(dCQ1))

# do the same for other questions

dTQ2 = convergeTreatmentColumns(dTQ2, 2)
dCQ2 = convergeControlColumns(dCQ2, 2)

dTQ3 = convergeTreatmentColumns(dTQ3, 3)
dCQ3 = convergeControlColumns(dCQ3, 3)

dTQ4 = convergeTreatmentColumns(dTQ4, 4)
dCQ4 = convergeControlColumns(dCQ4, 4)

dTQ5 = convergeTreatmentColumns(dTQ5, 5)
dCQ5 = convergeControlColumns(dCQ5, 5)

dTQ6 = convergeTreatmentColumns(dTQ6, 6)
dCQ6 = convergeControlColumns(dCQ6, 6)

# sanity check on column names for all datasets
identical(colnames(dTQ2), colnames(dCQ2))
identical(colnames(dTQ3), colnames(dCQ3))
identical(colnames(dTQ4), colnames(dCQ4))
identical(colnames(dTQ5), colnames(dCQ5))
identical(colnames(dTQ6), colnames(dCQ6))

# now that we have converged on column names, we should be able to merge all data sets in row major format
appendAllDataTables <- function(tableList) {
  obj <- deparse(substitute(tableList[1]))
  assign(obj, value = data.table::rbindlist(tableList), envir = .GlobalEnv)
}
  
dataset = appendAllDataTables(list(dTQ1, dTQ2, dTQ3, dTQ4, dTQ5, dTQ6, dCQ1, dCQ2, dCQ3, dCQ4, dCQ5, dCQ6))
```

```{r}
# AgeBin is a feature of interest for us, which tells us which age group the respondent belongs to
# We will infer this from the YearOfBirth variable

# First convert the variable to numeric
dataset$YearOfBirth = as.numeric(dataset$YearOfBirth)
# Get current age
dataset$Age = as.integer(format(Sys.Date(), "%Y")) - dataset$YearOfBirth
# Add a column called AgeBin
dataset$AgeBin = "NA"

# TODO: clean up - probably a better way to implement this
AssignAgeBin <- function(dt) {
  
  for (i in 1:nrow(dt)) {
    
          # we were able to parse the year as an int
          if (!is.na(dt[i]$Age) & is.numeric(dt[i]$Age) & dt[i]$Age > 0 & (floor(log10(dt[i]$YearOfBirth)) + 1) == 4) {
              # valid age, assign to category
              # we will keep things simple and have 6-12, 12-25, 25-40, 40-60, 60+
              # for age under 6, we assume that the age is invalid and need to be removed later
              if (dt[i]$Age <= 6) {
                dt[i]$AgeBin = NA
              } else if (dt[i]$Age <= 12) {
                dt[i]$AgeBin = "Child"
              } else if (dt[i]$Age <= 25) {
                dt[i]$AgeBin = "Student"
              } else if (dt[i]$Age <= 40) {
                dt[i]$AgeBin = "Adult"
              } else if (dt[i]$Age <= 60) {
                dt[i]$AgeBin = "MiddleAge"
              } else if (dt[i]$Age > 60) {
                dt[i]$AgeBin = "Senior"
              } else {
                dt[i]$AgeBin = NA
              }
          
          }
          else {
            # assign to NA
            dt[i]$AgeBin = NA
          }
    
  } # end of for loop
  
  return(dt)
}

dataset <- na.omit(dataset, cols="Age")
dataset <- AssignAgeBin(dataset)
dataset <- na.omit(dataset, cols="AgeBin")
```

